Title here

### 2016-09-14 portfolio/text/ms.Rmd
Finish bringing in mindmap (mostly discussion)

\noindent
Fig. \ref{fig:ts} - limited entry + movement towards salmon and specialization in Alaska

@@

\noindent
Something about overall model fit

@@

\noindent
Fig. \ref{fig:spokes} - add permits

@@

\noindent
Fig. \ref{fig:across} - across strategies

@@

\noindent
Fig. \ref{fig:within} - within strategies

@@

>>>>

### Fig. \ref{fig:ts} - limited entry + movement towards salmon and specialization in Alaska

@@

### Something about overall model fit

@@

### Fig. \ref{fig:spokes} - add permits

@@

### Fig. \ref{fig:across} - across strategies

@@

### Fig. \ref{fig:within} - within strategies

@@

### Take homes / summary

- What's novel
    - Huge dataset
    - Permit level data
    - Account for covariates
    - Accounting for strategies
    - Keeping annual data (not condensing to mean and cv)
    - Joint modelling
    - look at different mechanisms of diversification
- Suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost 
- Adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next
- not as simple as increase diversity (within permit) and reduce risk
- 2 dimensions to think about (revenue and variability); and the trade-off is fishery specific 
    - effects within a permit strategy are permit specific  
    - Importantly it's a tradeoff - 2 dimensions - sometimes make more money by specializing... Some highly variable single species permits make a ton of money... which preferable?

### Reconciling the effects at different levels of species diversity

- How fit in with K and H?
- Year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional diversification
- Risk results not really risk, but unpredictability given our covariates ...
don't change anything and it's most predictable how well you'll do
- What's unpredictable in our model, might be more predictable on a year to
year, species by species basis for individual permit holder
- Equilibrium, average variability vs year to year effect for one person

### Limitations + obvious extensions

- limitations...
- Vary by time
- Vary by mean diversity
- Spatial variation
- Nonlinear effects
- Response to specific events like EVOS and ITQs

### Implications for limited entry, ITQs, and catch shares

- if this is true, this is concerning because in many areas of the world and
fisheries, regulations and market forces have encouraged specialization 
- Permit diversity result: a privileged position - expensive to get to into
(quote king crab license) 
- Locking into permits limits ability to pick lower risk strategies and is
getting people locked into low diversity permits that may be doing well now,
but not necessarily always

### Conclusions + recommendations
